---
title: "Jace Innis' Dive Log"
description: This page shows my personal dive log and the dive log maintained with CSUMB’s dive program
output:
  distill::distill_article:
    css: styles.css
    highlight: rstudio
    toc: true
---



```{r include=FALSE}

library(rmarkdown)
library(distill)
library(dplyr)
library(lubridate)
library(stringr)

data = read.csv("dive.csv")

data$date = paste(data$year,data$month,data$day, sep = "-")

data = data[,c(14, 8, 9, 5:7, 10:13)]

data1 = read.csv("PersonalDivelog.csv")

s = table(c(data$Specific.Site, data1$Specific.Site))


```

### Dive statistics 
###### (calculated with r)

<center>
Total number of dives: `r nrow(data) + nrow(data1)`  
Total number of hours underwater: `r sum(data$Bottom.Time)/60+sum(data1$Bottom.Time)/60`  
Number of 'Cold water dives' : `r nrow(data)+nrow(filter(data1, Temp<16))`  
Number of hours 'Cold water dives' : `r sum(data$Bottom.Time)/60+sum(filter(data1, Temp<16)$Bottom.Time)/60`   
Number of unique dive sites `r length(s)`
</center>


## CSUMB Dive log

The table below shows all dives recorded with CSUMB, to include:   

* Dive Courses (Adv. & Res., Occup. Dive Tech., Sci. Diving Technique)  
* Senior project   
* Student Instruction Assistant 


```{r echo=FALSE, layout="l-page"}


paged_table(data , options = list(rows.print = 15))
  

```



## Personal Dive log

The table below shows my personal dive log (does not include CSUMB dives)


```{r include=FALSE}


data = read.csv("PersonalDivelog.csv")


data$Date = dmy(data$Date)

data = data %>% 
  arrange(desc(Date))

data$Date = paste0(day(data$Date),month(data$Date, label = TRUE),str_sub(data$Date, start = 3L, end = -7L))


data = data[,c(1:3,8,4,6:7)]

```


```{r echo=FALSE, layout="l-page"}


paged_table(data , options = list(rows.print = 15))
  
 
```















<!-- ```{css echo=FALSE} -->
<!-- d-title { -->
<!--     display: none; -->
<!--   } -->
<!-- ``` -->


