---
title: "Jace Innis' Dive Log"
output:
  distill::distill_article:
    css: styles.css
    highlight: rstudio
    toc: true
---



## CSUMB Dives


```{r include=FALSE}

library(rmarkdown)
library(distill)
library(dplyr)
library(lubridate)
library(stringr)

data = read.csv("dive.csv")

data$date = paste(data$year,data$month,data$day, sep = "-")

data = data[,c(length(data),5:(length(data)-1))]

data1 = read.csv("PersonalDivelog.csv")


```
The table below shows all dives recorded with csumb, to include:   

* courses (Rescue, Master, Sci Dive)   
* Senior project  
* Instruction assistant

Total number of dives: `r nrow(data)`

Number of hours underwater: `r sum(data$Bottom.Time)/60`


```{r echo=FALSE, layout="l-screen-inset"}


paged_table(data , options = list(rows.print = 15))
  

```



## Personal Dive log

The table below shows my personal dive log (dose not include CSUMB dives)

Total number of dives: `r nrow(data1)`

Total number of dives w/ temp < 16$^\circ$c : `r nrow(filter(data1, Temp<16))`

Number of hours underwater: `r sum(data1$Bottom.Time)/60`

Number of hours underwater w/ temp < 16$^\circ$c : `r sum(filter(data1, Temp<16)$Bottom.Time)/60`


```{r include=FALSE}


data = read.csv("PersonalDivelog.csv")


data$Date = dmy(data$Date)

data = data %>% 
  arrange(desc(Date))

data$Date = paste0(day(data$Date),month(data$Date, label = TRUE),str_sub(data$Date, start = 3L, end = -7L))


data = data[,c(1:4,6:8)]

```


```{r echo=FALSE, layout="l-screen-inset"}


paged_table(data , options = list(rows.print = 15))
  
 
```















<!-- ```{css echo=FALSE} -->
<!-- d-title { -->
<!--     display: none; -->
<!--   } -->
<!-- ``` -->


